\vspace{-2cm} \LARGE Divergence-Free Smoothed Particle Hydrodynamics \\ \large Advanced Simulation and Visualization of Fluids in Computer Graphics

### 2016-12-14 report/paper.tex
Adapted timestep

\title{\Large Advanced Simulation and Visualization of Fluids\\ in Computer Graphics \\ \large Divergence-Free Smoothed Particle Hydrodynamics}

\author{\begin{tabular}{ccc}
    Isabell Jansson & Ronja Grosz  & Jonathan Bosson \\
    \small isaja187@student.liu.se &\small rongr946@student.liu.se &\small jonbo665@student.liu.se \\
\end{tabular}}

@@

\documentclass[12pt, twocolumn]{article}

% Our packages
\usepackage{graphicx}   % Images
\usepackage{amsmath}    % Math
\usepackage{amssymb}    % Math
\usepackage{listings}   % To write code in latex
\usepackage{color}      % Custom colors

@@

\begin{document}
\twocolumn[
\begin{@twocolumnfalse}
\maketitle

\begin{abstract}
    This is the paper's abstract \ldots
    \\{\bf Index Terms:} Divergence-free, SPH, divergence correction, density correction.
\end{abstract}

\end{@twocolumnfalse}
]

@@

% CFL condition, explain why its necessary and how its assured that each rendered frame has the same time step.
In order to assure a stable simulation is it necessary to adapt the time step depending on the motion. The quicker the particles move the smaller time steps are taken such that the numerical error of the explicit time integration is negligible.

>>>>

\title{\vspace{-2cm} \LARGE Divergence-Free Smoothed Particle Hydrodynamics \\ \large Advanced Simulation and Visualization of Fluids in Computer Graphics}

\author{\begin{tabular}{ccc}
    Isabell Jansson\thanks{isaja187@student.liu.se} & Ronja Grosz\thanks{rongr946@student.liu.se}  & Jonathan Bosson\thanks{jonbo665@student.liu.se}
\end{tabular}}

@@

\documentclass[11pt, twocolumn]{article}

% Our packages
\usepackage{graphicx}   % Images
\usepackage{amsmath}    % Math
\usepackage{amssymb}    % Math
\usepackage{listings}   % To write code in latex
\usepackage{color}      % Custom colors
\usepackage{abstract}   % Onecolabstract, saythanks
\usepackage[margin=1.2in]{geometry}

\usepackage{bm}
\newcommand{\vect}[1]{\bm{#1}} % bold vector

\setlength{\columnsep}{20px} % Length between twocolumn

@@

\begin{document}
\twocolumn[
\maketitle

\begin{onecolabstract}
    \noindent This is the paper's abstract \ldots
    \vspace{1em}\\{\bf Index Terms:} Divergence-free, SPH, divergence correction, density correction.\vspace{1em}
\end{onecolabstract}
]
\saythanks

@@

% CFL condition, explain why its necessary and how its assured that each rendered frame has the same time step.
In order to assure a stable simulation it is necessary to adapt the time step depending on the motion. 
The quicker the particles move the smaller time steps are taken such that the numerical 
error of the explicit time integration is negligible. For this is a condition proposed by Courant–Friedrichs–Lewy used often refered as the CFL-condition show in equation \ref{eq:cfl}. The time step $\Delta t$ is equal to a fraction of the particle's diameter $d$ divided by the maximum velocity $\vect{V_{max}}$ in the scene.

\begin{equation}\label{eq:cfl}
\Delta t \leq \frac{0.4 \cdot d}{\vect{V_{max}}}
\end{equation}

Each rendered frame however have a constant time step in order to ensure no speed change in the playback of the rendered video. This is decided from the user side as a desired fps parameter. This means that the simulation loop can iterate multiple times within each frame adaptively depending on the maximum velocity.
